Revisited hidden weight bit function

### 2024-10-30 RevisedHiddenWeight.tex
Easier proof in Prop 11

   This leaves us with the following cases to consider for $(p,q,r;u,v)$:
    \begin{gather*}
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
    \end{gather*}
    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
    \[
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
    \]
    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
    \[
        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
    \]
    Writing $z=\cos\alpha+\mathrm i\sin\alpha$ and $z=\cos2\alpha+\mathrm i\sin2\alpha$, we have:
    \begin{align*}
        |-z^2+2z+1|^2&=|-z^2+2z+1|^2\\
        &=|-\cos2\alpha-\mathrm i\sin2\alpha+2\cos\alpha+2\mathrm i\sin\alpha+1|^2\\
        &=(-\cos2\alpha+2\cos\alpha+1)^2+(-\sin2\alpha+2\sin\alpha)^2\\
        &=6-2\cos(2\alpha);
    \end{align*}
    the last equality can be obtained by expanding and applying classical trigonometric identities, or by making use of a computer algebra system such as \textsc{SageMath}. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:

>>>>

   This leaves us with the following cases to consider for $(p,q,r;u,v)$:
    \begin{gather*}
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
    \end{gather*}
    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
    \[
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
    \]
    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
    \[
        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
    \]
    Writing $z=\ee^{\ii\alpha}$ and using that $|w|^2=w\overline w$ for every complex number $w$, we have:
    \begin{align*}
        |-z^2+2z+1|^2&=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right)\\
        &=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}\\
        &=6-2\cos2\alpha;
    \end{align*}
    the last equality uses that $\ee^{2\ii\alpha}=\cos2\alpha+\ii\sin2\alpha$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:
